Neuroevolution in a simple two-player game situation

### 2019-01-08 documentation/paper.tex
little clean-up

\subsection{Mutation}
Mutation is accomplished by adding Gaussian noise to a subset of all weights and biases. We selected an individual for mutation with a probability of $0.7$, which then had a per-neuron mutation rate of $0.5$, and a sigma of $0.01$.

@@

\todo{trainer5t does not coincide on the two graphs, what happened? We get a good result against trainer5t according to the bottom graph}

@@

We implemented a limited set of curriculum learning, where the training happens against increasingly harder opponents \texttt{gintonicV9\_5t}, \texttt{com\_11\_5t}, \texttt{gintonicV9}, and \texttt{com\_11} for 200 generations each. These bots previously worked as solid teachers. As can be seen on \ref{fig:change}, only the Per-individual self adaptation seems to work, there's no transfer of knowledge between the different bots for the other methods.

@@

A video of our two self-trained bots playing games can be found at \texttt{documentation/two_species.mp4}

@@

In the future we would like to improve on our best network by combining self train and the trainers, in order to produce an undefeated champion of the game. Since the project is open-source, we also plan on contributing some of our agents back to the original.

>>>>

\subsection{Mutation}
Mutation is accomplished by adding Gaussian noise to a subset of all weights and biases. We selected an individual for mutation with a probability of $0.7$, which then had a per-neuron mutation rate of $0.5$, and a standard derivation $\sigma=0.01$.

@@

@@

We implemented a limited set of curriculum learning, where the training happens against increasingly harder opponents \texttt{gintonicV9\_5t}, \texttt{com\_11\_5t}, \texttt{gintonicV9}, and \texttt{com\_11} for 200 generations each. These bots previously worked as solid teachers. As can be seen on \ref{fig:change}, only the per-individual self adaptation seems to work, there's no transfer of knowledge between the different bots for the other methods.

@@

A video of our two self-trained bots playing games can be found under the name \texttt{two\_species.mp4}

@@

In the future we would like to improve on our best network by combining self train and the trainers, in order to produce an undefeated champion of the game. Since the project is open-source, we also plan on contributing some of our agents back to the original.
This future work can be tracked on the GitHub repositoy in \cite{github_repo}.
